Measurement of CO2 from carbonate minerals using a hybrid sputter gas ion source with an open split interface

### 2021-08-18 doc/AMS-15/AMS15_abstract.Rmd
Add author

---
title: "Measurement of CO2 from carbonate minerals using a hybrid sputter gas ion source with an open split interface"
author:
- Brett Longworth
- Josh Burton
- Simon Pendleton
- Josh Hlavenka
- Sydney Moser
- Mark Roberts
output:
  word_document: default
  html_document: default
  pdf_document: default
---

>>>>

---
title: "Measurement of CO2 from carbonate minerals using a hybrid sputter gas ion source with an open split interface"
author:
- Brett Longworth
- Josh Burton
- Simon Pendleton
- Josh Hlavenka
- Sydney Moser
- Mark Roberts
- Mark Kurz
output:
  word_document: default
  html_document: default
  pdf_document: default
---
